---
title: "gi-ws-02-1"
author: "TLKoch, Balzern, s-johannes"
date: "13 November 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1


```{r}
structuralattribute <- c("canopy height", "understory structure", "understory density", "ground elevation")
response <- c("first return", "return count between first and last return", "density of the returning points", "last return")
spatialscale <- c("vertical", "vertical", "horizontal", "vertical")

df <- data.frame(structuralattribute,response,spatialscale)

library(knitr)
kable(df)

```

## 2
1) Create DEM and DSM from first and last returns

2) Canopy height --> subtract DEM from DSM

3) Understory structure --> count returns in between canopy and ground for different heights (vegetation foliage partly transmissive for the NIR used by lidar); create height classes (for example 0-1m, 1-2m,...) and assign the returns to the classes

4) Understory density: create a raster for each height class; summarize the raster pixels (return count) for each height and calculate the density



```{r}
DiagrammeR::mermaid("
graph LR
A(Create DEM and DSM) --> B(Canopy height)
    B --> C(Understory structure)
    C --> D(understory density)
")
   
```

## 3
### Problems

-	when the understory is very dense, the laser signal cannot reach the ground and thus the ground elevation value is too high
-	the top of a tree may not be hit by the laser signal resulting in a too low value of canopy height
- the understory density may not be comparable, because the canopy could have blocked many returns
